---
title: "Personal"
---

## Dining

From chicken nuggets at McDonalds to local halibut crudo at [The Progress](https://theprogress-sf.com/), I would love to talk about food with you...

From a [Nascar Spritz](https://punchdrink.com/articles/beer-spritz-spaghett-nascar-camparty/#:~:text=The%20NASCAR%20Spritz%20marries%20high,High%20Life%2C%20not%20Bud).), at bad-movie night with friends, to an Iguana Beach at [The Hub](https://thehubslo.com/), I would love to talk about drinks with you...

```{r}
#| echo: false
#| message: false
#| error: false
#| warning: false
library(tidyverse)
library(googlesheets4)
library(DT)

dining <- read_sheet("https://docs.google.com/spreadsheets/d/1SjECEhymMNzHyx2SfseH0AufspRfUTB_zPtQB9OW_wY/edit?gid=0#gid=0")

dining <- dining |>
  rename(
    Name = name,
    State = state,
    City = city,
    Meal = meal,
    `First Recommendation` = first_rec,
    `Second Recommendation` = second_rec,
    Website = website
  )
  
dining |>
  arrange(State, City) |>
  datatable(options = list(pageLength = 5))
```

## Travel

From Vava'u, Tonga to Omaha, Nebraska to Tromsø, Norway, I would love to talk about traveling with you...

```{r}
#| echo: false
#| message: false
#| error: false
#| warning: false
travel <- read_sheet("https://docs.google.com/spreadsheets/d/13S5UHSi4lezXp9S_IjJoRADRIkOUZ_susjKFXCMGdpY/edit?gid=0#gid=0")

travel <- travel |>
  rename(
    State = state,
    City = city,
    Country = country
  )
  
travel |>
  arrange(Country, City, State) |>
  datatable(options = list(pageLength = 5))
```

## Other Recreation

I am equal-opportunity when it comes to staying active: working out at the gym, hiking, video games, board games, tv, and movies.
