---
title: "Personal"
---

From chicken nuggets at McDonalds to local halibut crudo at The Progress, I would love to talk about food with you...

From a Nascar Spritz, at bad-movie night with friends, to an Iguana Beach at The Hub, I would love to talk about drinks with you...

```{r}
library(tidyverse)
library(googlesheets4)
library(DT)

dining <- read_sheet("https://docs.google.com/spreadsheets/d/1SjECEhymMNzHyx2SfseH0AufspRfUTB_zPtQB9OW_wY/edit?gid=0#gid=0")

dining <- dining |>
  rename(
    Name = name,
    State = state,
    City = city,
    Meal = meal,
    `First Recommendation` = first_rec,
    `Second Recommendation` = second_rec,
    Website = website
  )
  
dining |>
  datatable()
```

From Vavau, Tonga to Omaha, Nebraska to Tromso, Norway, I would love to talk about traveling with you...

```{r}
travel <- read_sheet("https://docs.google.com/spreadsheets/d/13S5UHSi4lezXp9S_IjJoRADRIkOUZ_susjKFXCMGdpY/edit?gid=0#gid=0")

travel <- travel |>
  rename(
    State = state,
    City = city,
    Country = country
  )
  
travel |>
  datatable()
```

I am equal-opportunity when it comes to staying active: working out at the gym, hiking, video games, board games, tv, and movies.
